Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-22 paper.qmd
chore: remove end of line extre whitespaces
chore: fix typo
fix: reword duplicated sentence

This call to `rix()` generates a `default.nix` file for a development shell that encapsulates 
a complete and reproducible research environment. It provides [R]{.proglang} and its packages 
(including [AER]{.pkg} at version 1.2-8), several TeXLive packages for \LaTeX document authoring, 
development versions of [rix]{.pkg} and [fusen]{.pkg} pulled directly from GitHub at a specific commit,
and the Positron editor. The reproducibility of this environment is guaranteed by pinning all 
components to a single point in time: the [R]{.proglang} packages are resolved from the CRAN 
snapshot of October 20, 2025, while all other system tools are fixed to the version of 
`nixpkgs` from that same date. Typing `nix-shell` in a terminal in the folder that containts
this `default.nix`, will drop the user into the shell. It should be noted that it is 
also possible to configure IDEs to dynamically load this shell to provide the right
tooling for developing.

>>>>

This call to `rix()` generates a `default.nix` file for a development shell that encapsulates
a complete and reproducible research environment. It provides [R]{.proglang} and its packages
(including [AER]{.pkg} at version 1.2-8), several TeXLive packages for \LaTeX document authoring,
development versions of [rix]{.pkg} and [fusen]{.pkg} pulled directly from GitHub at a specific commit,
and the Positron editor. The reproducibility of this environment is guaranteed by pinning all
components to a single point in time: the [R]{.proglang} packages are resolved from the CRAN
snapshot of October 20, 2025, while all other system tools are fixed to the version of
`nixpkgs` from that same date. Typing `nix-shell` in a terminal within the folder that contains
this `default.nix` will drop the user into a new shell. It should be noted that it uses the
`nixpkgs` from that same date. It is also possible to configure IDEs to dynamically load this
new shell to provide the proper development tooling.
